Automatically proving equivalence by type-safe reflection

### 2016-01-19 paper-JFP-DTP/content/1-introduction.tex
more fix

        \item The normalisation procedures are implemented by following a
        correct by construction approach, instead of implementing a
        normalization procedure, and proving afterwards that this function
        effectively computes a normal form. This approach is much more suitable
        for programming languages like Idris. Again, this approach will be
        presented in Section~\ref{sect:ideas} on the smaller problem, 
        and in Sections~\ref{sect:general} and~\ref{sect:reuse}
        for the complete hierarchy of algebraic structures.

        \item We develop a hierarchy of tactics where each tactic reuses the
        rewriting machinery from the structure immediately above in the hierarchy.
        For example,
        simplifying neutral elements is only implemented at the monoid level,
        and each level above monoid reuses it. Re-usability can be quite tricky
        to obtain when we want to reuse a prover from a structure which is less
        expressive. For example, reusing the monoid prover for building the
        group prover is not trivial, since we lose the possibility to express
        negations ($-x$) and minus operations ($x-y$). Some specific encodings
        will be presented in Section~\ref{sect:reuse} for solving this problem.

>>>>

        \item The normalisation procedures are implemented by following a
        correct by construction approach, instead of implementing a
        normalization procedure, and proving afterwards that this function
        is correct. This approach is much more suitable
        for programming languages like Idris. Again, this approach will be
        presented in Section~\ref{sect:ideas} on the smaller problem, 
        and in Sections~\ref{sect:general} and~\ref{sect:reuse}
        for the complete hierarchy of algebraic structures.

        \item We develop a hierarchy of tactics where each tactic reuses the
        rewriting machinery from the structure immediately above in the hierarchy.
        For example,
        simplifying neutral elements is only implemented at the monoid level,
        and each level above monoid reuses it. Re-usability can be quite tricky
        to obtain when we want to reuse a prover from a structure which is less
        expressive. For example, reusing the monoid prover for building the
        group prover is not trivial, since we lose the possibility to express
        negations ($-x$) and subtractions ($x-y$). Some specific encodings
        will be presented in Section~\ref{sect:reuse} for solving this problem.
